WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-19 paper/ms.tex
recompile

\acknowledgements
L.G.B.\ and J.N.W.\ gladly acknowledge helpful discussions with
A.~Bailey, F.~Dai, K.~Patra and V.~Van Eylen, and are grateful to the
people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks the TESS project and the Heising-Simons foundation for
supporting this work.
%
WASP-4 was included on the ``short-cadence'' target list thanks to the
Guest Investigator programs of J.\ Southworth and S.\ Kane (G011112
and G011183 respectively). 
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Verifying the TESS Time Stamps}
\label{sec:verify_tess}

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf There is no evidence for a systematic offset between TESS
			times and the barycentric reference.} While the WASP-4b transits
		fell about 82 seconds earlier than expected, other well-observed
		hot Jupiters, in particular WASP-6b and WASP-18b, arrived on time.
		Ticks are observed TESS transit midtimes; the orange distribution
		is a gaussian centered on zero with standard deviation
		($\sigma_{\rm predicted}$) calculated from the pre-TESS transit
		times.  The blue distribution is a gaussian centered on the
		weighted average of the TESS times, with width equal to the
		uncertainty in the mean, {\it i.e.}, the standard deviation
		of the TESS residual times divided by $\sqrt{N-1}$, with $N$ the
		number of transits.
		\label{fig:hjs}
	}
\end{figure*}

>>>>

\acknowledgements
L.G.B.\ and J.N.W.\ gladly acknowledge helpful discussions with
A.~Bailey, F.~Dai, J.~Goodman, K.~Patra and V.~Van Eylen, and are
grateful to the people who have turned TESS from an idea into reality.
%
J.N.W.\ thanks the TESS project and the Heising-Simons foundation for
supporting this work.
%
WASP-4 was included on the ``short-cadence'' target list thanks to the
Guest Investigator programs of J.\ Southworth and S.\ Kane (G011112
and G011183 respectively). 
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
This research has made use of the NASA Exoplanet Archive, which is
operated by the California Institute of Technology, under contract
with the National Aeronautics and Space Administration under the
Exoplanet Exploration Program.
%
This work made use of NASA's Astrophysics Data System Bibliographic
Services.
%
This research has made use of the VizieR catalogue access tool, CDS,
Strasbourg, France. The original description of the VizieR service was
published in A\&AS 143, 23.
%
This work has made use of data from the European Space Agency (ESA)
mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed
by the {\it Gaia} Data Processing and Analysis Consortium (DPAC,
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding
for the DPAC has been provided by national institutions, in particular
the institutions participating in the {\it Gaia} Multilateral
Agreement.
%
\newline
%
\facility{
	TESS \citep{ricker_transiting_2015},
	Gaia \citep{gaia_collaboration_gaia_2016,gaia_collaboration_gaia_2018}
}
%
\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  \texttt{astropy} \citep{the_astropy_collaboration_astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  \texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{corner} \citep{corner_2016},
  \texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{IPython} \citep{perez_2007},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001}.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Verifying the TESS Time Stamps Using Other Hot Jupiters}
\label{sec:verify_tess}

\begin{figure*}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.98\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf There is no evidence for a systematic offset between TESS
			times and the barycentric reference.} While the WASP-4b transits
		fell about 82 seconds earlier than expected, other well-observed
		hot Jupiters, in particular WASP-6b and WASP-18b, arrived on time.
		Ticks are observed TESS transit midtimes; the orange distribution
		is a gaussian centered on zero with standard deviation
		($\sigma_{\rm predicted}$) calculated from the pre-TESS transit
		times.  The blue distribution is a gaussian centered on the
		weighted average of the TESS times, with width equal to the
		uncertainty in the mean, {\it i.e.}, the standard deviation
		of the TESS residual times divided by $\sqrt{N-1}$, with $N$ the
		number of transits.
		\label{fig:hjs}
	}
\end{figure*}
